{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }

### 2017-09-18 Meetings/AUGrelated/mst1_tfm_200917.tex
Started MST1-TFM presentation and change of figures

\documentclass[10pt, compress]{beamer}
\usetheme[conference=Topic 21,venue=Remote, date=15/09/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: AUG experiment analsysis meeting }}
\date{15 September 2017}
\author[N. Vianello]{N. Vianello and V. Naulin for the
  Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Summary of the campaigns}
  \begin{itemize}[<+-|alert@+>]
  \item L-Mode experiment, CW 17.
    \begin{enumerate}
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
    \end{enumerate}    
    \item H-Mode experiment, CW 21. 
      \begin{enumerate}
    \item<2> Compare divertor/midplane fueling effect on filamentary
      transport and profiles without cryo-pumps
    \item<2> Compare profiles with the same fueling with/without cryopums
    \item<2> Determine an H-Mode with the cryopumps matching similar
      divertor pressure and SOL profiles
    \end{enumerate}
  \end{itemize}    
\end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-TFM,venue=Remote, date=20/09/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
\date{20 September 2017}
\author[N. Vianello]{N. Vianello and V. Naulin for the
  Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Summary of the campaigns}
  \begin{itemize}
  \item<1-> L-Mode experiment, Calendar week
    17. It will constitute baseline scenarios to be replicated on
    the other MST1 devices. \textcolor{ta3scarletred}{Operation without cryopumps}
    \begin{enumerate}
      \item<1-> \color<2->{ta3chameleon}{Performed similar density ramps in an I$_p$ scan at constant q$_{95}$}
      \item<1-> \color<2->{ta3chameleon}{Performed similar density ramps in an I$_p$ scan at
        constant B$_t$}
      \item<1-> \color<2->{ta3chameleon}{Prepare scenarios for H-Mode operation}
      \end{enumerate}
    \item<3-> H-Mode experiment, CW 21. 
      \begin{enumerate}
      \item<3-> \color<4->{ta3scarletred}{Compare divertor/midplane fueling effect on filamentary
        transport and profiles without cryo-pumps}
      \item<3-> \color<4->{ta3chameleon}{Compare profiles with the same fueling with/without cryopums}
      \item<3-> \color<4->{orange}{Determine an H-Mode with the cryopumps matching similar
        divertor pressure and SOL profiles}
      \end{enumerate}
    \end{itemize}    
  \end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
